\subsection{Tensors}
\subsubsection{Covariant Tensors}
We had earlier defined to be a multi-linear map, blah blah. We will now focus on tensors of type $(0,k)$ which is also called a covariant tensor of rank $k$. Thus,
$$t_p = \bigotimes_{i=1}^k T_p\SM\rightarrow \re$$
So, it will take $k$ tangent vectors and map it to a real number. It must also satisfy multilinearity, that is, linearity in each argument:
$$t_p(\ldots, a\ v_p + b\ w_p,\ldots ) = a \ t_p(\ldots,v_p,\ldots ) + b\ t_p(\ldots,w_p,\ldots ) $$
The set of all $(0,k)$ tensors denoted by $T_p^{(0,k)}\SM$ forms a real vector space. Let $a,b\in \re$ and $t_p, s_p\in T_p^{(0,k)}\SM$, then for all $v_{ip}\in T_p\SM, \ i=1,2,\ldots,k$, we have:
$$(a\ t_p+b\ s_p)(v_{1p}, \ldots, v_{kp})\equiv a\ t_p(v_{1p}, \ldots, v_{kp})+b\ s_p(v_{1p}, \ldots, v_{kp})$$ 
To check that this is indeed another tensor, we need to check for multilinearity. For that,
\begin{itemize}
    \item Let $v_p, w_p\in T_p\SM$ be two vectors. Then,
    \begin{align*}
        (a t_p+b s_p)(v_{1p} \ldots, v_{ip} + w_{ip}\ldots v_{kp})&\equiv a\ t_p(v_{1p}\ldots, v_{ip} + w_{ip} \ldots v_{kp})+b\ s_p(v_{1p} \ldots v_{ip} + w_{ip} \ldots v_{kp})\\
        &=a\ (t_p(v_{1p}\ldots v_{ip} \ldots v_{kp})+t_p(v_{1p}\ldots, w_{ip} \ldots v_{kp}))\\&\qquad \qquad+b\ (s_p(v_{1p} \ldots v_{ip} \ldots v_{kp})+s_p(v_{1p} \ldots w_{ip} \ldots v_{kp}))\\
        &=(a t_p + b s_p) (v_{1p}\ldots v_{ip} \ldots v_{kp}) + (a t_p + b s_p) (v_{1p}\ldots, w_{ip} \ldots v_{kp})
    \end{align*}
\item Let $c\in \re, v_{ip}\in T_p\SM$. Then,
\begin{align*}
    (a t_p+b s_p)(v_{1p} \ldots, cv_{ip}\ldots v_{kp})&\equiv a\ t_p(v_{1p}\ldots, c v_{ip} \ldots v_{kp})+b\ s_p(v_{1p}\ldots, c v_{ip} \ldots v_{kp})\\ &= c(a\ t_p(v_{1p}\ldots,v_{ip} \ldots v_{kp})+b\ s_p(v_{1p}\ldots,v_{ip} \ldots v_{kp}))\\
    &=c (at_p+bs_p)(v_{1p}\ldots,v_{ip} \ldots v_{kp})
\end{align*}
\end{itemize}
Thus, from these two conditions, we can conclude the condition for multi-linearity. 
\subsubsection{Tensor Product}
We can form a product of two tensors, not neccessarily of the same rank. For that, let $t_p\in T_p^{(0,k)}\SM, s_p\in T_p^{(0,l)}\SM$. Then the tensor product is defined as:
$$(t_p\otimes s_p)(v_{1p},\ldots, v_{k+l,p})\equiv t_p(v_{1p},\ldots,v_{kp})s_p(v_{k+1,p},\ldots,v_{k+l,p})$$ 
Using this, we can say that \[t_p\otimes s_p: \bigotimes_{i=1}^{k+l}T_p\SM\rightarrow \re\] And checking for multilinearity will be easy (as well as boring). Hence we directly declare that it is a $(k+l)$ rank covariant tensor. \\[0.2cm]
\textbf{Properties of Tensor Product:} 
\begin{itemize}
    \item \textcolor{blue}{Tensor product is distributive}.\\[0.2cm]
    \textit{Proof.} Let us take three covariant tensors $t_1, t_2$ of rank $k$ and $s$ of rank l at point $p$ and let $(v_1,\ldots,v_{k+1})$ be a vector. Then,
    \begin{align*}
        &((at_1+bt_2)\otimes s) (v_1,\ldots,v_{k+1})\\
        &=(at_1+bt_2)(v_1,\ldots,v_k)s(v_{k+1},\ldots,v_{k+l})\\
        &=(at_1(v_1,\ldots,v_k)+bt_2(v_1,\ldots,v_k))s(v_{k+1},\ldots,v_{k+l})\\
        &=at_1(v_1,\ldots,v_k)s(v_{k+1},\ldots,v_{k+l})+bt_2(v_1,\ldots,v_k)s(v_{k+1},\ldots,v_{k+l})\\
        &=(a(t_1\otimes s) + b(t_2\otimes s))(v_1,\ldots,v_{k+1})
    \end{align*}
    Similarly, we can prove that if it had been a linear combination in the right tensor $\sim s_1+s_2$ and hence we conclude the distributive property.
    \item \textcolor{blue}{Tensor product is associative}.\\[0.2cm]
    \textit{Proof.} Let $r\in T^{(0,k)}_p\SM,s\in T^{(0,l)}_p\SM,t\in T^{(0,m)}_p\SM$. Then r\otimes (s\otimes t) and (r\otimes s)\otimes t are both $(k+l+m)$ rank tensor. Now, we have:
    \begin{align*}
        (r\otimes(s\otimes t))(v_1, \ldots, v_{k+l+m}) &= r(v_1,\ldots,v_k) (s\otimes t)(v_{k+1},\ldots,v_{k+l+m})\\
        &=r(v_1,\ldots,v_k) s(v_{k+1},\ldots,v_{k+l})t(v_{k+l+1},\ldots,v_{k+l+m})\\[0.2cm]
        ((r\otimes s)\otimes t)(v_1, \ldots, v_{k+l+m}) &= (r\otimes s)(v_1,\ldots,v_{k+l}) t(v_{k+l+1},\ldots,v_{k+l+m})\\
        &=r(v_1,\ldots,v_k) s(v_{k+1},\ldots,v_{k+l})t(v_{k+l+1},\ldots,v_{k+l+m})
    \end{align*}
    Since both these expressions are equal, we proved the associativity.
\end{itemize}
\subsubsection{Sometimes all that we need is a coordinate...}
Remember that any tangent vector can be written as:
$$v_p = v_p[x^i]\qty(\pdv{x^i})_p = dx_p^i(v_p)\qty(\pdv{x^i})_p$$
Then we can write the action of the tensor in the following way:
\begin{align*}
    t_p\qty(v_1,\ldots v_j \ldots ,v_k) &= t_p\qty( dx^{i_1}_p(v_1)\qty(\pdv{x^{i_1}})_p, \ldots dx^{i_j}_p(v_j)\qty(\pdv{x^{i_j}})_p)\ldots dx^{i_k}_p(v_k)\qty(\pdv{x^{i_k}})_p\\
    &=t_p\qty(\qty(\pdv{x^{i_1}})_p, \ldots \qty(\pdv{x^{i_j}})_p \ldots \qty(\pdv{x^{i_k}})_p) \prod\limits_{m=1}^k dx^{i_m}_p(v_m)
\end{align*}
The second line follows from the multilinearity of tensors. Also, note that $\prod\limits_{m=1}^k dx^{i_m}_p(v_m)$ can be written as $ \displaystyle \qty(\bigotimes_{m=1}^k dx^{i_m}_p)(v_1,\ldots,v_k)$ (basically, each $dx^{i_m}_p$ acts on the corresponding $v_m$ and we get the product thingy). Thus, we obtain:
\begin{align*}
    t_p\qty(v_1,\ldots v_j \ldots ,v_k) &= \qty(\mathcolor{OliveGreen}{t_{p,i_1i_2\ldots i_k}}\ \bigotimes_{m=1}^k dx^{i_m}_p)(v_1,\ldots,v_k)
\end{align*}
where, $$\mathcolor{OliveGreen}{t_{p,i_1i_2\ldots i_k}} = t_p\qty(\qty(\pdv{x^{i_1}})_p, \ldots \qty(\pdv{x^{i_j}})_p \ldots \qty(\pdv{x^{i_k}})_p)$$ Note that this is not a single quantity. Owing to Einstein's convention, the sum over all the indices has been nicely hidden from the above expression (and even then it looks so ghastly! \emoji{skull}). However, there are indeed $n^k$ sums and hence these are $n^k$ numbers, which are the coordinates of the tensor $t_p$ in the coordinate system. \footnote{Physicists do all sort of weird stuffs with these components only. For them, tensor means these components.}\\[0.2cm]
From this, we finally have:
$$t_p = t_{p,i_1i_2\ldots i_k} \ \bigotimes_{m=1}^k dx^{i_m}_p$$
Now, suppose we have two set of coordinate functions (that is, we have two charts $(U,\phi)$ and $(U',\phi')$ and we consider $p\in U\bigcup U'$) given by $(x^1,\ldots, x^n)$ and $(x'^1,\ldots, x'^n)$. Then we can write:
$$t_p = t_{p,i_1i_2\ldots i_k} \ \bigotimes_{m=1}^k dx^{i_m}_p = t'_{p,i_1i_2\ldots i_k} \ \bigotimes_{m=1}^k dx'^{i_m}_p$$
Now, 
\begin{align*}
     t'_{p,i_1i_2\ldots i_k} &=  t_p\qty(\qty(\pdv{x'^{i_1}})_p, \ldots \qty(\pdv{x'^{i_j}})_p \ldots \qty(\pdv{x'^{i_k}})_p)\\
&=\qty(t_{p,j_1j_2\ldots j_k} \ \bigotimes_{m=1}^k dx^{j_m}_p)\qty(\qty(\pdv{x'^{i_1}})_p, \ldots \qty(\pdv{x'^{i_j}})_p \ldots \qty(\pdv{x'^{i_k}})_p)\\
&=t_{p,j_1j_2\ldots j_k} \prod\limits_{m=1}^k dx_p^{j_m}\qty(\qty(\pdv{x'^{i_{m}}})_p)
\end{align*}
Now, note the following notational jugglery: $dx_p^{j_q}\qty(\qty(\pdv{x'^{i_q}})_p)\equiv \qty(\pdv{x'^{i_q}})_p[x^{j_q}] \equiv \qty(\pdv{x^{j_q}}{x'^{i_q }})_p$
Using this we again have something nice:
$$t'_{p,i_1i_2\ldots i_k} =t_{p,j_1j_2\ldots j_k} \ \prod\limits_{m=1}^k \qty(\pdv{x^{j_m}}{x'^{i_m }})_p$$
We obtain the transformation rule for covariant tensors (yes, the rule that was apparently a definition of tensors, has now been derived explicitly, just from a simple definition of tensor as a multi-linear map!). 
\subsubsection{Tensor Field}
A $\mqty(0\\k)$ tensor field $t$, like vector field, assigns a tensor to each point $p\in \SM$. If $t$ is a tensor field and $X_1, \ldots, X_k$ are vector fields, then $t(X_1, \ldots, X_k)$ is a function whose value at $p\in \SM$ is:
$$t(X_1,\ldots,X_k)(p) = t_p(X_{1p}, \ldots, X_{kp})$$
If $X_i \in \mathfrak{X}(\SM) \implies t(X_1, \ldots, X_k)\in \cty{M}$, then it is called a differentiable tensor field.\\[0.2cm]
Now, we define the components of a tensor field as the $n^k$ functions:
$$t_{i_1 \ldots i_k}\equiv t\qty(\qty(\pdv{x^{i_1}}),\ldots,\qty(\pdv{x^{i_k}}))$$
Then using this definition we can write:
\begin{align*}
    t(X_1,\ldots,X_k) &= t\qty(X_1^{i_1}\qty(\pdv{x^{i_1}}),\ldots, X_k^{i_k}\qty(\pdv{x^{i_k}}))\\
    &=t\qty(\qty(\pdv{x^{i_1}}),\ldots,\qty(\pdv{x^{i_k}})) X_1^{i_1}\ldots X_k^{i_k}\\
    &=t_{i_1 \ldots i_k} \ X^{i_1}_1\ldots X^{i_k}_k
\end{align*}
We can now say that the tensor field is differentiable iff the component functions are smooth. \\[0.2cm]
\textbf{Some definitions...}\\[0.2cm]
If $s,t$ are $\mqty(0\\k)$ tensor fields, $a,b\in\re$ and $f$ is a function on $\SM$, we define, $$(at+bs)_p := at_p + bs_p \qquad (ft)_p = f(p) t_p$$
If $m$ is a $\mqty(0\\k)$ tensor field and $r$ is a $\mqty(0\\l)$ tensor field, then $(m\otimes r)_p\equiv m_p\otimes r_p$ is a $\mqty(0\\k+l)$ tensor field. \\
\begin{align*}
    t(p) = t_p &= t_p\qty(\qty(\pdv{x^{i_1}})_p, \ldots,\qty(\pdv{x^{i_k}})_p) \ dx_p^{i_1}\otimes \ldots \otimes dx_p^{i_k}\\
    &=t\qty(\qty(\pdv{x^{i_1}}), \ldots,\qty(\pdv{x^{i_k}}))(p) \ dx^{i_1}(p)\otimes \ldots \otimes dx^{i_k}(p)\\
    &=\qty(t\qty(\qty(\pdv{x^{i_1}}), \ldots,\qty(\pdv{x^{i_k}})) \ dx^{i_1}\otimes \ldots \otimes dx^{i_k})(p)
\end{align*}
Thus, we obtain: 
$$t \equiv t\qty(\qty(\pdv{x^{i_1}}), \ldots,\qty(\pdv{x^{i_k}})) \ dx^{i_1}\otimes \ldots \otimes dx^{i_k}$$
 We can show that the tensor field is a $\SC^\infty$ multi-linear map, that is, $f,g: \SM\rightarrow \re$ and $\{X_i\}_{i=1}^k, Y_i$ are vector fields, then:
 $$t(X_1,\ldots fX_i+gY_i, \ldots X_k) = ft(X_1,\ldots X_i, \ldots X_k) + gt(X_1,\ldots  Y_i, \ldots X_k)$$
 The converse of this statement is also true, that is, any map $t$ following this property, is a $\mqty(0\\k)$ tensor field. 


\subsubsection{Contravariant Tensors} 
This thing is very, very, very similar to the covariant tensors. A contravariant tensor of type $\mqty(k\\0)$ (rank $k$) at a point $p\in \SM$ is a multi-linear map taking $k$ covectors as input and returning a real number, that is,
$$\prod_{i=1}^{k}T_p^*\SM \rightarrow \re$$
Since any covector can be expanded as $\alpha = \alpha\qty(\qty(\pdv{x^i})_p)dx^i_p$, we can then write:
\begin{align*}
    t_p(\alpha_1,\ldots,\alpha_k) &= t_p\qty(\alpha_1\qty(\qty(\pdv{x^{i_1}})_p)dx^{i_1}_p,\ldots, \alpha_k\qty(\qty(\pdv{x^{i_k}})_p)dx^{i_k}_p)\\
    &=t_p(dx^{i_1}_p,\ldots, dx^{i_k}_p) \alpha_1\qty(\qty(\pdv{x^{i_1}})_p)\ldots \alpha_k\qty(\qty(\pdv{x^{i_k}})_p)\\
    &=t_p^{i_1,\ldots,i_k}\qty(\pdv{x^{i_1}})_p(\alpha_1)\ldots \qty(\pdv{x^{i_k}})_p(\alpha_k)\\
    &=\qty(t_p^{i_1,\ldots,i_k} \qty(\pdv{x^{i_1}})_p \otimes \ldots \otimes\qty(\pdv{x^{i_k}})_p)(\alpha_1,\ldots,\alpha_k)
\end{align*}
Thus, we obtain:
$$t_p \equiv t_p^{i_1,\ldots,i_k} \qty(\pdv{x^{i_1}})_p \otimes \ldots \otimes\qty(\pdv{x^{i_k}})_p$$
The set of all $\mqty(k\\0)$ tensors at $p\in \SM$, denoted by $T_p^{(k,0)}\SM$ is a vector space, as before.

\subsubsection{Mixed Tensors}
This is a general tensor of type $\mqty(k\\l)$, multi-linearly mapping $k$ covectors and $l$ vectors at point $p\in\SM$ to a real number. Thus, 
$$t_p: \prod_{i=1}^{k}T_p^*\SM\prod_{i=1}^{l}T_p^\SM \rightarrow \re$$
This is what we had earlier defined, before being engulfed by differential geometry, however, we did not have the slightest indication of the beauty of this definition, since we were not familiar with the formalism. \\[0.2cm]
The set of $\mqty(k\\l)$ tensor forms a vector space $T_p^{(k,l)}\SM$ and we can also similarly define the tensor product between a $\mqty(k\\l)$ and a $\mqty(k'\\l')$ tensor, resulting in a $\mqty(k+k'\\l+l')$ tensor. A basis for the space $T_p^{(k,l)}\SM$ is given by:
$$\bigotimes_{d=1}^k \qty(\pdv{x^{i_d}})_p\ \otimes \ \bigotimes_{d=1}^l dx_p^{j_d}$$
As $i_d$ and $j_d$ can take n values, the space is $n^{k+l}$ dimensional. \footnote{Note that if $k=l=0$, we will have a $\mqty(0\\0)$ tensor which is actually a function on $\SM$}
\subsubsection{General Tensor Fields}
Similarly to covariant tensor field, we can define the contravariant tensor field. In terms of the coordinates, we can write a $\mqty(k\\0)$ tensor field $t$ in the form,
$$t = t(dx^{i_1},\ldots,dx^{i_k})\qty(\pdv{x^{i_1}})\otimes\ldots\otimes\qty(\pdv{x^{i_k}})$$
The tensor field is smooth if $t(\alpha_1, \ldots, \alpha_k)\in \cty{\SM}$ whenever $\alpha_i\in \Lambda^1\SM$ which happens iff the $n^k$ functions $t(dx^{i_1},\ldots,dx^{i_k})$ are smooth.\\[0.2cm]
Mixed tensor fields can be similarly defined. The set of all smooth $\mqty(k\\l)$ tensor fields $T^k_l(\SM)$ is a module over the ring $\cty{\SM}$
A tensor field is completely characterised by the $n^{k+l}$ component functions, 
$$\tensor{t}{_{i_1,\ldots,i_k}^{j_1,\ldots,j_l}} = t\qty(\qty(\pdv{x^{i_1}}),\ldots,\qty(\pdv{x^{i_k}}), dx^{j_1},\ldots,dx^{j_l})$$
Now, \begin{align*}
    t(X_1,\ldots,X_k, \omega_1,\ldots,\omega_l) &= \tensor{t}{_{i_1,\ldots,i_k}^{j_1,\ldots,j_l}} dx^{i_1}(X_1)\ldots dx^{i_k}(X_k)\pdv{x^{j_1}} (\omega_1)\ldots {x^{j_l}} (\omega_l)\\
    &=\tensor{t}{_{i_1,\ldots,i_k}^{j_1,\ldots,j_l}}  dx^{i_1}\otimes dx^{i_k}\otimes \pdv{x^{j_1}}\otimes\ldots\otimes \pdv{x^{j_l}}(X_1, \ldots,X_k,\omega_1,\ldots, \omega_l)
\end{align*}
Thus we obtain:$$t=\tensor{t}{_{i_1,\ldots,i_k}^{j_1,\ldots,j_l}}  \qty(dx^{i_1}\otimes dx^{i_k}\otimes \pdv{x^{j_1}}\otimes\ldots\otimes \pdv{x^{j_l}})$$
Using this, we can then obtain the transformation rule for the tensor:
$$\tensor{{t'}}{_{a_1\ldots a_k}^{b_1\ldots b_k}} = \pdv{x^{i_1}}{x'^{a_1}}\ldots  \pdv{x^{i_k}}{x'^{a_k}} \pdv{x^{b_1}}{x'^{j_1}}\ldots  \pdv{x^{b_l}}{x'^{j_l}}\tensor{{t}}{_{i_1\ldots i_k}^{j_1\ldots j_l}} $$
